---
title: "Normal and others"
author: "Dr K"
date: "February 27, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Normal and other distributions

Among all the distributions we see in practice, one is overwhelmingly the most common.
The symmetric, unimodal, bell curve is ubiquitous throughout statistics. Indeed it is so
common, that people often know it as the normal curve or normal distribution.
The normal distribution model always describes a symmetric, unimodal, bell-shaped curve.
However, these curves can look different depending on the details of the model. Specifcally,
the normal distribution model can be adjusted using two parameters: mean and standard
deviation. As you can probably guess, changing the mean shifts the bell curve to the left or
right, while changing the standard deviation stretches or constricts the curve.
Lets explore how we can produce plots of a couple of different normal distributions.  First we construct the x-axis

```{r}
xaxis = seq(from=-200,to=200,by=.1)
boxplot(xaxis)
```

now we create the yaxis by using one of the distribution functions helper functions the dnorm function.  We will look at a normal distribution with mean = 110 and standard deviation = 15

```{r}
yaxis1 = dnorm(x=xaxis, mean = 110, sd=15)
```
now we plot it

```{r}
plot(xaxis,yaxis1,col="blue")

```

lets create a second yaxis2 with mean 95 and standard deviation = 25

```{r}
yaxis2 = dnorm(x=xaxis, mean = 45, sd=25)
plot(xaxis,yaxis2,col="green")
```

Lets put both on the same plot to compare

```{r}
plot(xaxis,yaxis1,col="blue")
lines(xaxis,yaxis2,col="green")
```
  
What is the area under each curve  


```{r}
(area1=sum(yaxis1*.1))
(area2=sum(yaxis2*.1))
```

