---
title: "Normal and others"
author: "Dr K"
date: "February 27, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tigerstats)
require(tidyverse)
```

## Normal and other distributions

Among all the distributions we see in practice, one is overwhelmingly the most common.
The symmetric, unimodal, bell curve is ubiquitous throughout statistics. Indeed it is so
common, that people often know it as the normal curve or normal distribution.
The normal distribution model always describes a symmetric, unimodal, bell-shaped curve.
However, these curves can look different depending on the details of the model. Specifcally,
the normal distribution model can be adjusted using two parameters: mean and standard
deviation. As you can probably guess, changing the mean shifts the bell curve to the left or
right, while changing the standard deviation stretches or constricts the curve.
Lets explore how we can produce plots of a couple of different normal distributions.  First we construct the x-axis

```{r}
xaxis = seq(from=-200,to=200,by=.1)
histogram(xaxis)
```

now we create the yaxis by using one of the distribution functions helper functions the dnorm function.  We will look at a normal distribution with mean = 110 and standard deviation = 15

```{r}
yaxis1 = dnorm(x=xaxis, mean = 110, sd=15)
```
now we plot it

```{r}
plot(xaxis,yaxis1,col="blue")

```

lets create a second yaxis2 with mean 95 and standard deviation = 25

```{r}
yaxis2 = dnorm(x=xaxis, mean = 45, sd=25)
plot(xaxis,yaxis2,col="green")
```

Lets put both on the same plot to compare

```{r}
plot(xaxis,yaxis1,col="blue")
lines(xaxis,yaxis2,col="green")
```
  
What is the area under each curve  


```{r}
(area1=sum(yaxis1*.1))
(area2=sum(yaxis2*.1))
```
##Now we look at a way that normal distributions occur naturally.

We examine what happens when we are interested in averages.   First we get the collection of ten thousand opinions on Kim Kardashian from the tigerstats package in R.

```{r}
head(imagpop)
kim <- imagpop$kkardashtemp
```

The variable "kim" is a rating on a scale from zero to 100 of each persons perception of Kim.  Lets look at that distribution.

```{r}
plot(kim)
plot(density(kim))
hist(kim)
```
  
##Wow this is about as far from normal as you get!!!

looks like about half luv her and the other half think she stinks.

We will now use the ggplot2 plotting software from the tidyverse collection of packages to get some more insight.

```{r}
ggplot(imagpop,aes(x=kkardashtemp,col=sex)) +
  geom_histogram()

```
  
##guys like her, gals dish her!  

Now we look at average group opinions.  We start with groups of two and work our way up to bigger groups.

```{r}
by2=numeric()
for (i in 1:10000){
 by2[i] = mean(sample(kim,size=2))
}
plot(density(by2))
```

##Whats going on??? 
looks like it is twice as likely to select a guy and a gal as two guys or two gals.

##Lets try 3   
  
```{r}
by3=numeric()
for (i in 1:10000){
 by3[i] = mean(sample(kim,size=3))
}
plot(density(by3))
```
  

## Thats cool, Lets try 4  

```{r}
by4=numeric()
for (i in 1:10000){
 by4[i] = mean(sample(kim,size=4))
}
plot(density(by4))
``` 
  
##As we take larger and larger sample sizes the shape of the plot of averages is transforming into a bell shaped curve.
When the sample sizes reach 30 the sample averages morph into a normal distribution -
this result is called "The Central Limit Theorem"
 
```{r}
by30=numeric()
for (i in 1:10000){
 by30[i] = mean(sample(kim,size=30))
}
plot(density(by30))
```  
 
##We used dnorm to create the points in our plot, what do pnorm, qnorm, and rnorm do???